Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-26 paper/v1.0/sections/5_floquet_drude_conductivity.tex
More corrections

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Refs.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimensional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

@@

where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate by considering each matrix elements separately

@@

Since we can diagonalize the impurity averaged Green's function using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}, and we evaluate the matrix element of the difference between retarded and advanced Green's functions

@@

using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}. Using the matrix elements of electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain

@@

and the only non-zero term would be

@@

Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property

@@

  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll},

@@

and using central element ($l=0$) of the inverse scattering time matrix we can modify the derived conductivity expression

@@

with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. We already identified that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction. However, by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify

@@

Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for this system

@@

where $k_B$ is Boltzmann constant, $T$ is absolute temperature and $\varepsilon_F$ is Fermi energy of the system. Considering the above distribution with extremely low temperature conditions we can approximate

@@

Same as above derivation we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}

>>>>

A general theory for the conductivity in dressed systems with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity has been discribed by
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimensional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states. Moreover, $tr[\cdot]$ is the trace of operator.

@@

where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate as follows

@@

Since we can diagonalize the impurity averaged Green's functions using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as

@@

Here we used the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}. Applying the matrix elements of the electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we can obtain

@@

and after the expansion, the only remaining non-zero term would be

@@

Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy, and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}, we can identify the following property

@@

  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll}.

@@

Then using central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression as follows

@@

where $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$. We already identified that the inverse scattering time matrix's central element is independent of $k_x$ value and we can get the sum over all available momentum space in $x$ direction.
However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify that

@@

Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system

@@

where $k_B$ is Boltzmann constant, $T$ is absolute temperature and $\varepsilon_F$ is Fermi energy of the system. Considering the above distribution with extremely low temperature conditions, we can approximate

@@

Same as above derivation, we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}
